% Chapter 6

\chapter{Related Work} % Main chapter title
\label{Related Work} % For referencing the chapter elsewhere, use \ref{Chapter1} 
The related work section presented in this thesis, focuses on the state of the art in Cloud Computing in regard to it's monitoring, scheduling and SLA management capabilities. Therefore this chapter was divided into five categories, namely: (1) Infrastructure Measurements and Cloud Monitoring, (2) SLA Description Languages, (3) Performance Prediction, (4) Scheduling Mechanisms and (5) SLA Enforcement.

\section{Infrastructure Measurements and Cloud Monitoring}
Cloud Computing today delivers nearly unlimited scalable on demand computing resources within a few clicks. But the monitoring and government of such resources may come with some requirements. Monitoring is one of the fundamental parts of every cloud platform, since monitoring is needed to scale applications or instances correctly based on their resource utilization. It is also need to detect and discover defects and limitations, such as bottlenecks in the infrastructure environment. Additionally monitoring can give viable insights to both Cloud users and providers by revealing usage patterns and trends. Without any form of monitoring Cloud providers would not even be able to invoice their customer correctly, since they would not be able to tell how much ressouces and for how log the customer has used them. Cloud Monitoring has many ties into different Cloud Management fields such as capacity and resource planning and management, SLA management, incident management and troubleshooting, performance management and billing. An early example towards distributed resources monitoring is NetLogger \cite{DBLP:conf/mascots/2000}, a distributed monitoring system, which could monitor and collect network information. Published in 2000, application could use NetLoggers API to gather load information of the network and react accordingly. With GridEye \cite{Fu:2006:GSG:1170138.1170724} a service-oriented monitoring system, with an flexible, scaleable architecture and forecasting algorithm for performance prediction on the basis of traditional MA(k) and ExS(alpha) models was purposed. In 2009 Sandpiper \cite{Wood:2009:SBG:1663647.1663710} was proposed, a system, which automatically could monitor and detect hotspots and based on that remap or reconfigure VMs if necessary. The described system marks a first step towards autonomous SLA management, since the internal remaping algorithm considered SLA violations and to avoid them. 
In recent years various academic and commercial Cloud monitoring solutions have been proposed. In 2014 Jonathan Stuart Ward and Adam Barker \cite{ward2014observing} published a taxonomy of Cloud Monitoring stating scalability, cloud awareness, fault tolerance, aromaticity, comprehensiveness, timeliness and multiply granularity as core requirements towards effective Cloud monitoring. Fatema et al. \cite{fatema2014survey} and Aceto et al. \cite{aceto2013cloud} analized the most common open source and commercial monitoring solutions, such as Nagios, Collectd, Ganglia, IBM Tivoli, Amazon Cloud Watch, Azure Watch, PCMONS, mOSAIC, CASViD and many more, according on how they relate with these requirements. Recently Manasha Saqib \cite{saqib2017cloud} apportioned these requirements along the seven layers of Cloud Computing accoring to \cite{CSA3.0} \cite{spring2011monitoring1} \cite{spring2011monitoring2}: Facility, Network, Hardware, Operating System (OS), Middleware, Application and User. These studies provided a comprehensive overview of the available monitoring tools and their ability to support Cloud operational management, but also stated their shortcomings in the different areas. Cloud Monitoring in this thesis is considered as an enablement technology. The proposed architecture and algorithms are able to work with different monitoring solutions. The main focus thereby lies within the acquisition and enhancement ot such methodologies with additional information.
An additional topic especially in the area of PaaS is the application monitoring and application performance monitoring in the cloud.The definition of application performance management by Menasce \cite{menasce2002load}: APM is a collection of management processes used by organizations to ensure that the QoS of their e-business applications meets the business goals. So APM directly aims at the application lifecycle and management processes such as monitoring, resource management, performance-management, reporting and so on, of software systems. According to Gartner \cite{GartnerAPM} there are severall established big names in APM such as IBM, Oracle, BMC and so on, that are getting challenges by innovative start-ups such as AppDynamics or Dynatrace, and Correlsense. APM can be used as performance analysis and monitoring agents in SaaS and PaaS, and as such will be an topic for future work.


\section{SLA Modeling and Description Languages}
----
SLA attributes and its criteria are investigated for cloud computing by Alhamad et al. \cite{5610586}. This study determined the individual SLA metrics for SaaS, PaaS and IaaS separately. Although specific metrics are presented based on their layer requirements, they never considered the SLAs relation and hierarchical nature of cloud computing. 

Patel et al. \cite{Patel2009ServiceLA} proposed the WSLA framework for SLA enforcement in cloud computing while this structure already proposed for SOA by Keller and Ludwing \cite{Ludwig03WSLA}. This framework is not enough adapted for cloud needs. Cloud computing nature and requirements are totally different from SOA therefore SLA management systems cannot directly be brought from SOA. 

Some other frameworks such as RESTful \cite{Kubert:2011:RIW:1967428.1967444}, SALmonADA \cite{6225938}, SLA@SOI \cite{slasoi2011} have put aside the hierarchical nature of cloud computing. They have directly applied the SLA structure in the cloud computing area from SOA and grid computing. 

The SSV architecture proposed by Kertesz et al. \cite{5739040}which contracted the SLA between an individual service provider and consumer after the negotiation process. However, they did not consider the hierarchical relation of SLAs in the cloud environment. 

Although a research by Undheim et al. \cite{6076508} attempted to deploy the on demand SLAs with QoS details on different levels, it followed the common SLA structure with stated shortcomings. 

Different techniques of SLA negotiation including direct, broker and market based negotiations are investigated and compared by Grandits et al. [29] while they did not have enough attention to the related SLAs in negotiation process. So, the output of these techniques is the isolated agreed SLA. 


-----

NIST \cite{Liu2011} has also pointed out the necessity of SLAs, SLA management, definition of contracts, orientation of monitoring on Service Level Objects (SLOs) and how to enforce them. However a clear definition of a reference of a specific format is missing. This is also the case with the Internet Engineering Task Force (IETF) \cite{Khasnabish2010}. Besides these approaches of the companies and organisations there are further efforts to develop and to realize cloud management architectures and systems. A basic discussion can be found in the book from Wieder et.al. \cite{Wieder2011} mainly concerned about SLA definitions and negotiations.

In 2003 IBM developed the Web Service Agreement Language (WSAL) \cite{Ludwig03WSLA} which is still available in the Version 1.0 that dates back to the same year. It has not been further developed since. WSAL focused on performance and availability metrics. It seriously lacks expression therefore it is not powerful enough. The required flexibility is also missing which is needed for dynamical changes at run time. It is closely connected to their XML schema and not very useful to determine conclusion.
WSAL has been mainly developed for Web services, its usage in other fields is questionable. It shows significant shortcomings regarding content as it focusses mainly on technical properties. The structural requirements, however, are met as discussed in Spillner et.al. \cite{Spillner2009}.

The WS-Agreement (WS-A) was developed by the Open Grid Forum in the year 2007 (Version 1.0) The last update which was based on the work of the European SLA@SOI project was done in 2011. Its advantages are the expandability and the adaptability which is, on the other hand, also one of its greatest disadvantages because it has not been specified in details by Kearney \cite{Kearney2011b}. It is based on technical transformation, the structural transformations, however, have not been taken into account.

The Foundation of Self Governing ICT Infrastructures (FOSll)-Project \cite{fosii} is another research project which aims at the usage of autonomic principals for information and communication systems. Self determining infrastructures should be realized and made available through cloud based services. Within the LoM2HiS autonomic SLA management is realized by translation of system parameters to abstract KPIs and SLOs  \cite{Brandic:2009:VFE:1616056.1616063}. The SLA specification is based on WSAL. The Texo project \cite{texo2011} attempts within the THESEUS research program to realize a conception of service descriptions, contract management, end to end marketplaces and monitoring from a business perspective. In addition the development and use of WS-A based SLAs are needed. Looking at the cloud interfaces that describe the management of resources within the cloud, it becomes obvious that they are exclusively designed with the purpose of system monitoring. They do not provide a direct monitoring of SLAs. Therefore the placement of machine readable SLAs is extremely difficult. This is also the case with existing monitoring tools.

SLA handling in clouds, resulting from the EU project OPTIMIS, is discussing negotiating and creating Service Level Agreements between infrastructure providers and service providers \cite{Lawrence:2010:USL:2050107.2050112}.
Although it is enhanced within the SLA@SOI project \cite{slasoi2011} its development is unclear because the SLA@SOI project develop its own format SLA@SOI SLA(T) \cite{slasoiwiki} and supported by the European IT industry. A comprehensive project result has been published on their web page. No independent analysis of the advantages or disadvantages of the SLA(T) format is available at the moment. It provides all structural requirements of a SLA and it has the greatest intersection with regard to content. SLA(T) is the basis of the proposed approach in this paper. Further it should be accentuated that a meta model SLA* \cite{slasoisrc} is defined which simplifies the extension and adaptability for SLA(T).

\section{Performance Prediction}
Neural Networks are widely used in forecasting problems. One of the earliest successful application of ANNs in forecasting is reported by Lapedes and Farber \cite{LapedesFarber87}. They used a feed-forward neural network with deterministic chaotic time series generated by the Glass-Mackey equation, to predict such dynamic non-linear systems.
Artificial Neural Networks are proven universal approximators \cite{Hornik1989359}\cite{Hornik1991251} and are able to forecast both linear \cite{Zhang20011183} and non-linear time series \cite{Zhang199835}. Adya and Collopy investigated in the effectiveness of Neural Networks (NN) for forecasting and prediction \cite{neural1}. They came to the conclusion that NN are well suited for the use of prediction, but need to be validated against a simple and well-accepted alternative method to show the direct value of this approach. Since forecasting problems are common to many different disciplines and diverse fields of research, it is very hard to be aware of all the work done in this area.  Some examples are forecasting applications such as: temperature and weather \cite{Langella2010328}\cite{Buizza}\cite{Roebber}, tourism \cite{Pattie1996151}, electricity load \cite{Park76685}\cite{Hippert910780}, financial and economics \cite{Bodyanskiy20061357}\cite{McAdam2005848}\cite{Kaastra1996215}\cite{Guresen201110389} and medical \cite{Vukicevic2014}\cite{Arizmendi20145296} to name a few. Zhang, Patuwo, and Hu \cite{Zhang199835} show multiple other fields where prediction by ANN was successfully implemented.

%While NNs powerful approximation capabilities and selfadaptive data driven modelling approach allow them great flexibility in modelling time series data, it also complicates substantially model specification and the estimation of their parameters. Direct optimisation through conventional minimisation of error is not possible under the multilayer architecture of NNs and the back- propagation learning algorithm has been proposed to solve this problem (Rumelhart, Hinton, & Williams, 1986), later discussed in the context of time series by Werbos (1990). Several complex training (optimisation) algorithms have appeared in the literature, which may nevertheless be stuck in local optima (Hagan, Demuth, & Beale, 1996; Haykin, 2009). To alleviate this problem, training of the networks may be initialised several times and the best network model selected according to some fitting criteria. However, this may still lead to suboptimal selection of parameters depending on the fitting criterion, resulting in loss of predictive power in the out-of-sample set (Hansen & Salamon, 1990). Another chal- lenge in the parameter estimation of NNs is due to the uncertainty associated with the training sample. Breiman (1996a) in his work on instability and stabilization in model selection showed that sub- set selection methods in regression, including artificial neural net- works, are unstable methods. Given a data set and a collection of models, a method is defined as unstable if a small change in the data results in large changes in the set of models.

Similar research with different focus has been conducted in the past for the use of machine learning in cloud environments. Prevost et al. used a Neural Network (NN), as well as a Linear Predictor \cite{prevost2011prediction} to anticipate future workloads by learning from historical URL requests. Although both models were able to give efficient predictions, the Linear Predictor was able to predict more accurately. Li and Wang proposed their modified Neural Network algorithm nn-dwrr in \cite{li2014sla}. The application of this algorithm led to a lowered average response time compared to application of traditional capacity based algorithms for scheduling incoming requests to VMs. In similar research Hu et al. \cite{hu2013kswsvr} have shown that their modification of a standard Support Vector Regression (SVR) algorithm can lead to an accurate forecasting of CPU Load what can be used to achieve a better resources utilization. Another algorithm, which is renowned for providing good results in similar scenarios, is Linear Regression. Although the results are often weaker compared to Neural Networks or Support Vector Machines (SVM) in cases of workload prediction \cite{bankole2013predicting} \cite{imam2011neural}, the fast training and deployment time of models built with Linear Regression should not be underestimated. Those examples show that there are a variety of optimization challenges in cloud environments which can be tackled by applying machine learning algorithms. What separates the current work from previous research is a detailed examination of specific characteristics of three different machine learning algorithms and presenting the results in a visual way. The choice to evaluate Neural Networks, Support Vector Machines and Linear Regression was made because those algorithms earned promising results in previously conducted research.


\section{Scheduling Mechanisms}

Most commonly found scheduling approaches for the Cloud, like proposed by Mao and Humphrey \cite{6114435} or Panda et al. \cite{PANDA2015176}, aim towards resource optimization based task scheduling. Therefore, cloud instances are regarded as computing tasks that have to be processed within certain resource constraints. However, this basic view is only suitable for cloud operations with already known tasks or performance requirements. In the real cloud environment, however, these are usually of no importance since cloud customers either do not know them or they are highly variable. The approach shown seems to have more applicability in grid computing.


Haizea \cite{haizea2} is a resource manager or resource scheduler. Haizea  can manage a set of computers (typically a cluster), allowing users to request exclusive use of those resources described in a variety of terms, such as "I need 10 nodes, each with 1 GB of memory, right now" or "I need 4 nodes, each with 2 CPUs and 2GB of memory, from 2pm to 4pm tomorrow". Haizea provides reservation and deadline sensitive type of leases along with the traditional immediate and best effort policies \cite{haizea1} \cite{haizea3} \cite{haizea4}. Haizea uses simple allocation policies for deadline sensitive leases. It tries to find out a single slot of required time between startTime and endTime of the given lease which can allocate the requested resources. If it is unable to ?nd such a time slot, it rejects the lease. 

\section{SLA Enforcement}




Boniface et al. [3] discuss dynamic service provisioning using GRIA SLAs. The authors describe provisioning of services based on agreed SLAs and the management of the SLAs to avoid violations. Their approach is limited to Grid environments. Moreover, they do not detail how the low-level metric are monitored and mapped to high-level SLAs. 

Comuzzi et al. \cite{5175897} define the process for SLA establishment adopted within the EU project SLA@SOI framework. The authors propose the architecture for monitoring SLAs considering two requirements introduced by SLA establishment: the availability of historical data for evaluating SLA offers and the assessment of the capability to monitor the terms in an SLA offer.


SLAs-LoM2HiS framework
The LoM2HiS framework comprises two core components, namely host monitor and run-time monitor. The former is responsible for monitoring low-level resource metrics, whereas the latter is responsible for metric mapping and SLA
violation monitoring. In order to explain our mapping approach we consider
the Service Level Objectives (SLOs) as shown in Table 1, including incoming
bandwidth, outgoing bandwidth, storage, and availability.
As shown in Figure 1, we distinguish between host monitor and run-time
monitor. Resources are monitored by the host monitor using arbitrary monitoring tools such as Ganglia [27]. Resource metrics include downtime, uptime, and
available storage. Based on the predefined mapping rules stored in a database,
monitored metrics are periodically mapped to the SLA parameters. An example
of an SLA parameter is service availability Av, (as shown in Table 1), which is
calculated using the resource metrics downtime and uptime and is defined by
the following the mapping rule: As described in a previous work [14], we implemented a highly scalable framework for mapping Low Level Resource Metrics to High Level SLA Parameters
(LoM2HiS framework) facilitating the exchange of large numbers of messages.
We designed and implemented a communication model based on the Java Messaging Service (JMS) API [21], which is a Java Message Oriented Middleware
API for sending messages between two or more clients. We use Apache ActiveMQ
as a JMS provider that manages sessions and queues.


-----


The LoM2HiS framework introduced by Emeakaroha et al. \cite{ [emeakaroha2010low] } as a part of FOSII \cite{fosii} infrastructure. They tried to map the low level metrics into high level SLA by their monitoring method but the common SLA is used and they followed the centralized monitoring system \cite{articleEmeakaroha2013}. The LoM2HiS monitoring framework is located in FoSII infrastructure which calculated the SLA attributes value based on the proposed metrics and formula \cite{articleEmeakaroha2013}. In this framework, the SLAs consist of attributes, metrics and formulas have to be located in a central repository.  Then, another monitoring system is used to measure the SLA validity. 

---
Another related work is DeSVi architecture by Emeakaroha et al. \cite{EMEAKAROHA20121017}, it is designed based on LoM2HiS \cite{5547150} framework which limited for only one data centre as an IaaS. 

----
The QoSMONaaS approach \cite{articleQoSMONaas} focused to the QoS monitoring as a service. Although this flexible approach is a third party SLA monitoring system, it still needs the external service for SLA validating.


-----
The violation reaction process is rarely discussed in the mentioned SLA monitoring frameworks.  The most of monitoring systems just tried to report the detected violations \cite{6225938} \cite{5175897} or assess the penalty cost of service providers \cite{10.1007/978-3-642-22709-7_46} \cite{Dastjerdi:2012:DOA:2275356.2275360}.

However, an effective reaction process is needed to react against SLA violations. Some studies such as \cite{6212007}, \cite{6150077} and \cite{WANG20121135} utilized the SLAs to manage the provider resources without any reaction against violations. 

The FoSII and DeSVi frameworks introduced by Emeakaroha et al. \cite{ [fosii] }\cite{EMEAKAROHA20121017}. They applied the monitoring, analysis, planning and execution loop
(MAPE) model to enforce the self-healing cloud computing. This architecture has beneficial for cloud management but not for sudden violation reaction. In another study, the LoM2HiS \cite{ [emeakaroha2010low] } framework tried to predict the SLA violations by predefining the thresholds. Then, the alerts are notified into the internal knowledge component for possible adjustment in provider resource [35] however there were not any other reaction strategies. 

On the other hand, LAYSI \cite{5614035} has propagated the detected SLA violations into upper layer but its communication model was based on subscription between meta-negotiators, brokers
and automatic service deployed. This reaction model was complex and followed the plain SLA document structure which is in contrast of selfhealing SLA. 

This literature review has illustrated that the related works and proposed solutions did  not suitably cover the cloud computing requirements. The most of related works have transmitted the SLA monitoring framework into cloud computing from SOA and grid computing. Although a few effective SLA monitoring and reacting mechanisms have presented, they have followed the common SLA structure yet. Having the selfhealing SLA in cloud computing, an effective selfmonitoring SLA and reaction mechanism are needed.



Slaws
Specs
EUROPEAN COMMISSION DIRECTORATE GENERAL COMMUNICATIONS NETWORKS, CONTENT AND TECHNOLOGY UNIT E2 - SOFTWARE AND SERVICES, CLOUD
https://www.sla-ready.eu/sla-negotiation

\section{Autonomic Computing}
Autonomic computing refers to the ability of a distributed system to manage its resources with little or no human intervention. It's all about creating a system that can intelligently adapt to changing environments and needs without the user even knowing it. It was launched in 2001 by IBM to reduce the complexity of managing large distributed systems \cite{horn2001autonomic}.


%This (autonomic computing) was instituted in cloud computing to address the challenges of cloud computing. Autonomic cloud computing helps address challenges related to QoS by ensuring SLA are met. QoS is maintained by mostly scaling up or down resources automatically depending on demand by client's business. In addition, autonomic cloud computing helps reduce the carbon footprint of data centres and cloud consumers by automatically scaling up or down energy usage base on cloud activity. Autonomic monitoring are mostly implemented on specific layers of the cloud computing architecture. Authors in [10] implemented an autonomic management system on the PaaS to ensure SaaS layer meets SLA, energy efficiency and maintains security. Authors in [11] developed fuzzy Q-Learning for knowledge evolution. It is a self-learning. Self-adapting cloud controller that auto scales (down or up) the number of virtual machines that support the cloud. It uses data collected at run-time and automatically continues to tune the data in order to achieve desired goals. This is particularly favourable, when there is not enough knowledge at design time. Additionally [12] implemented a QoS autonomic information delivering system for delivering agricultural information systems to farmers. This was achieved at IaaS layer using Cuckoo optimisation algorithm and fuzzy logic to attain autonomic resource allocation. Reference [13] presented a decentralised autonomic architecture for managing wireless sensor networks. They identified automatic operation, aware operation and adaptive operation as properties that each autonomic system must have. An automatic operation property ensures that the system can control its functions and internal resources without human intervention. Aware operation property allows the system to be aware of its resources and capabilities, this allows the system to monitor itself and use feedback mechanism to adapt to its environment. Adaptive operation property allows the system to continuously adapt to environment on short term

Autonomic computing in the area of cloud computing

Autonomic resource allocation 
\cite{inproceedingshu2009}
\cite{Casalicchio:2013:ARP:2494621.2494623}

Autonomic self-testing
\cite{5463688}


Autonomic life-cycle management





%----------------------------------------------------------------------------------------
% links and stufff
%
%
%http://www.sla-ready.eu/ SLA Ready EU Projekt
%http://www.cloudwatchhub.eu/
%
%http://www.specs-project.eu/
%
%ISO/IEC CD 19086-1  Information technology -- Cloud computing -- Service level agreement (SLA) framework and Technology -- Part 1: Overview and concepts
%
%ISO/IEC NP 19086-2 Information technology -- Cloud computing -- Service level agreement (SLA) framework and Technology -- Part 2: Metrics
%
%ISO/IEC 27004:2009 Information technology -- Security techniques -- Information security management -- Measurement
%
%ISO/IEC FDIS 27017 Information technology -- Security techniques -- Code of practice for information security controls based on ISO/IEC 27002 for cloud services
%
%NIST Cloud Computing Service Metrics Description http://www.nist.gov/itl/cloud/upload/RATAX-CloudServiceMetricsDescription-DRAFT-20141111.pdf
%
%Standards terms and performance criteria in service level agreements for cloud computing services - http://www.sla-ready.eu/sites/default/files/Finalreport.pdf

