%
% file: dedication.tex
% author: V?ctor Bre?a-Medina
% description: Contains the text for thesis dedication
%

\chapter*{Dedication and acknowledgements}
\begin{SingleSpace}
This work was made possible due to funding from the Federal Ministry of Education and Research of Germany and the Faculty of Computer Science at Furtwangen University. I wish to thank both organisations for their support. I would like to thank all team members at the Cloud Research Lab Furtwangen and the Plymouth CSCAN group for their support.\\

I would like to express my special appreciation and thank my Director of Studies, Dr. Christoph Reich for his tireless effort in steering me through the PhD process and for encouraging my research and for allowing me to grow as a research scientist.  Thanks also go to my supervisors, Dr. Nathan Clarke and Dr. Martin Knahl, who have spent a lot time proof reading papers and my thesis, in addition to providing helpful experience and guidance throughout my studies.  Additionally, i would like to thank all my colleagues at Furtwangen University for the excellent working atmosphere, their professionalism and support. \\

A very big thank you goes to my Mum and my Dad  for supporting me through out my entire life, as well as my entire family.You are the source of my joy and happiness, and words cannot express how grateful I am. Lastly, i would  like to thank all of my friends who supported me during this time, and incented me to strive towards my goal. 
\end{SingleSpace}
\clearpage

